%%
\documentclass[savetrees,12pt]{article}

\usepackage[pdftex]{graphicx}
\usepackage{amsmath}
%\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{subfigure}
\usepackage{natbib}
\usepackage{url}
\usepackage[lined,algonl,ruled]{algorithm2e}
\usepackage{geometry}
%\usepackage{algorithm}
\usepackage{listings}

\usepackage{pdfpages}
\usepackage[utf8]{inputenc}

\geometry{
    body={6.5in, 8.5in},
	left=1.0in,
	top=1.2in
}

\newcommand{\mbm}[1]{\mbox{\boldmath $#1$}}


\begin{document}

\title{Practice Feed-forward Nets}
\author{50DT057}
\date{Due on 01.03.2018}
%% use optional labels to link authors explicitly to addresses:
%% \author[label1,label2]{<author name>}
%% \address[label1]{<address>}
%% \address[label2]{<address>}
\maketitle

\section{Tensor Flow Introduction}
Install \verb+tensorflow+ for CPU/GPU depending on your hardware. Follow the low-level API tutorial here: \url{https://www.tensorflow.org/programmers_guide/low_level_intro}. 

\section{Learning to XOR}
In this example, we want to replicate the network from section 6.1. in the book. Using the code from the previous problem as a starting point do the following:
\begin{itemize}
\item Modify the input data and ground truth labels to hold the four data points for XOR on vectors in $\mathbb{R}^2$. 
\item Add one hidden layer to the model, with a ReLU activation function. Consult the API at \url{https://www.tensorflow.org/api_docs/python/}.
\item Train the network. How many iterations does it take to converge and what weights / biases do you converge to?
\item (optional) Add tensorboard visualization for the graph and the loss. See \url{https://www.tensorflow.org/programmers_guide/summaries_and_tensorboard}.
\item Try adding units to the hidden layer. How is the performance affected? What if you add more layers?
\item Try different optimizers (Adagrad and Adam) and different learning rates.
\item (optional) What if you use a different activation function?
\item (optional) What happens when your input vector is in $\mathbb{R}^3$?
\end{itemize}

\section{Classification}
Try out the tutorial on high-level TF API for feed-forward classification: \url{https://www.tensorflow.org/get_started/premade_estimators}.


\end{document}

